Towards Compiler-Agnostic Performance in Finite-Difference Codes

### 2015-10-01 docs/papers/shallow_performance/shallow_perf.tex
Final minor changes to paper text.

In common with OP2, the \psykal\ approach separates out the science
code and the performance related code and does this via a separate
layer. The calls that specify parallelism in both approaches are
similar in terms of where they are placed in the code and in their
semantics but the \psykal\ approach supports the specification of more
than one Kernel in a parallel region of code, compared with one for
OP2, giving more scope for optimisation. Another difference is that
the description metadata is provided with the Kernel in the \psykal\
approach whereas it is provided as part of the Kernel call in OP2.

>>>>

In common with OP2, the \psykal\ approach separates out the science
code and the performance related code via separate layers. The calls
that specify parallelism in both approaches are similar in terms of
where they are placed in the code and in their semantics but the
\psykal\ approach supports the specification of more than one kernel
in a parallel region of code, compared with one for OP2, giving more
scope for optimisation. Another difference is that the description
metadata is provided with a kernel in the \psykal\ approach whereas it
is provided as part of the kernel call in OP2.
